---
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(rvest)
library(flextable)
library(officer)

source('LossSummary.R')
WRloss <- cumulative_loss %>% filter(species == 'Winter-run') %>%
  summarize(maxloss = max(cumul_loss)) %>% pull()
partial <- temp %>% filter(confirmed == 'PARTIAL') %>%
  group_by(confirmed) %>%
  summarize(sum(loss)) %>% pull()
partial <- ifelse(length(partial) == 0, 0, partial)
SHloss <- cumulative_loss %>% filter(species == 'Steelhead') %>%
  summarize(maxloss = max(cumul_loss)) %>% pull()
WRtriggers <- sum(wr_weekly$triggered == "Yes")
SHtriggers <- sum(SH_weekly$triggered == "Yes")
```

Hi all,

Please see summary of most recent loss estimates at salvage facilities. Total annual loss of natural Winter-run Chinook Salmon as of `r format(Sys.Date() - 1, "%B %d, %Y")` is **`r WRloss - partial`** and loss of unconfirmed Winter-run Chinook Salmon is **`r partial`**. Total annual loss of CCV steelhead as of `r format(Sys.Date() - 1, "%B %d, %Y")` is **`r SHloss`**.  There have been **`r WRtriggers`** triggers of the Winter-run and **`r SHtriggers`** triggers of the steelhead distributed weekly loss thresholds in the past week (see table).

`r weekly_table`
<div style="text-align: center;">
```{r, fig.width=8, fig.height=5, fig.align='center', echo = FALSE}
loss_graph



