---
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(rvest)
library(flextable)
library(officer)

#source('assessment_STARS_update.R')
source('historic_graphs.R')
source('loss_summary.R')
source('Tillotson/tillotsonv4.R')
WRloss <- cumulative_loss %>% filter(species == 'Winter-run') %>%
  summarize(maxloss = max(cumul_loss)) %>% pull()
partial <- temp %>% filter(confirmed == 'PARTIAL') %>%
  group_by(confirmed) %>%
  summarize(sum(loss)) %>% pull()
partial <- ifelse(length(partial) == 0, 0, partial)
SHloss <- cumulative_loss %>% filter(species == 'Steelhead') %>%
  summarize(maxloss = max(cumul_loss)) %>% pull()
WRtriggers <- sum(wr_weekly$triggered == "Yes")
SHtriggers <- sum(SH_weekly$triggered == "Yes")
```
**WINTER-RUN GRAPHS**

Figure. STARS prediction with 80% CIs.
```{r echo=FALSE, fig.height=4, fig.width=7, warning=FALSE, eval = FALSE}
STARS_plot

```

Figure. Cumulative Count of current and historic Genetic WR
```{r, fig.width=7, fig.height=4, echo = FALSE, warning = FALSE}
spaghetti_wr

```

Figure. Histogram of historic genetic winter-run salvage
```{r, fig.width=7, fig.height=4, echo = FALSE, warning = FALSE}
genetics
```

Figure. Summary of WY 2025 loss of CCV steelhead and wild and hatchery winter-run
```{r, fig.width=8, fig.height=10, echo = FALSE, warning = FALSE}
combined_graph
```

Figure. Tillotson predictions at different OMRI scenarios for winter-run
```{r, fig.width=10, fig.height=6, echo = FALSE, warning = FALSE}
tillotson_graph
```
### SACPAS TABLES
TABLE X. Winter-run weekly distributed loss threshold.Last updated `r format(Sys.time(), '%m/%d/%Y')`
```{r, echo = FALSE, warning = FALSE}
flextable(wr_table)%>%
  vline()%>%
  hline() %>%
  border_outer() %>%
  width(width = 1, unit = "in") %>%
  font(fontname = 'Segoe UI', part = "body") %>%
  font(fontname = 'Segoe UI Semibold', part = "header") %>%
  fontsize(size = 12, part = "header") %>%
  fontsize(size = 10, part = "body")
```
TABLE. Historic migration and salvage patterns.Last updated `r format(Sys.time(), '%m/%d/%Y')`
```{r, echo = FALSE, warning = FALSE}


samt_url <- "https://www.cbr.washington.edu/sacramento/workgroups/salmon_monitoring.html"
page <- read_html(samt_url)

tables <- page %>% 
  html_nodes("table") %>%
  html_table(fill = T) 

table_historic <- tables[[4]] %>%
  dplyr::bind_rows() %>%
  janitor::clean_names(case = "upper_camel")

table_historic <- data.frame(lapply(table_historic, function(x) {gsub("BY", " BY", x)})) 
table_historic <- data.frame(lapply(table_historic, function(x) {gsub("WY", " WY", x)})) 
```

```{r, echo = FALSE, warning = FALSE}
flextable(table_historic) %>%
  vline()%>%
  hline() %>%
  border_outer() %>%
  width(width = 1, unit = "in") %>%
  font(fontname = 'Segoe UI', part = "body") %>%
  font(fontname = 'Segoe UI Semibold', part = "header") %>%
  fontsize(size = 12, part = "header") %>%
  fontsize(size = 10, part = "body")
```


```{r, echo = FALSE, warning = FALSE}
wr_till <- "https://www.cbr.washington.edu/sacramento/cohort/include_wrc/load_plot_tillotson_predicted_loss-1.png"
wr_historic <- "https://www.cbr.washington.edu/sacramento/cohort/include_wrc/load_plot_count_genetic_lad_loss-1.png"
```
!["Winter Run Loss Plot"](`r wr_till`)
!["Winter Run Historic Loss"](`r wr_historic`)

**STEELHEAD THINGS**

```{r, echo = FALSE, warning = FALSE}
filter(table_historic, grepl('Steelhead', Species)) %>%
  flextable() %>%
  vline()%>%
  hline() %>%
  border_outer() %>%
  width(width = 1, unit = "in") %>%
  font(fontname = 'Segoe UI', part = "body") %>%
  font(fontname = 'Segoe UI Semibold', part = "header") %>%
  fontsize(size = 12, part = "header") %>%
  fontsize(size = 10, part = "body")
```
  
TABLE X. Steelhead weekly distributed loss threshold.Last updated `r format(Sys.time(), '%m/%d/%Y')`
```{r, echo = FALSE, warning = FALSE, eval = FALSE}
flextable(SH_table)%>%
  vline()%>%
  hline() %>%
  border_outer() %>%
  width(width = 1, unit = "in") %>%
  font(fontname = 'Segoe UI', part = "body") %>%
  font(fontname = 'Segoe UI Semibold', part = "header") %>%
  fontsize(size = 12, part = "header") %>%
  fontsize(size = 10, part = "body")
```

Figures from SacPAS for steelhead
```{r, fig.width=7, fig.height=4, echo = FALSE, warning = FALSE}

sh_historic <- "https://www.cbr.washington.edu/sacramento/cohort/include_stlhd/load_plot_count_cumulative_loss-1.png"

sh_tillotson <- "https://www.cbr.washington.edu/sacramento/cohort/include_stlhd/load_plot_tillotson_predicted_loss-1.png"

sh_histogram <- "https://www.cbr.washington.edu/sacramento/cohort/include_stlhd/load_plot_count_total_loss-1.png"

```
!["Steelhead historic loss"](`r sh_historic`)
!["Steelhead sacpas tillotson"](`r sh_tillotson`)
!["Steelhead clipped and unclipped loss by year"](`r sh_histogram`)

Figure. SH cumulative loss
```{r, fig.width=7, fig.height=5, echo = FALSE, warning = FALSE}
sh_loss_graph
```

Figure. Histogram of historic clipped and unclipped steelhead salvage
```{r, fig.width=7, fig.height=5, echo = FALSE, warning = FALSE}
sh_all_graph
```

Figure. Tillotson predictions for steelhead at different OMRI scenarios
```{r, fig.width=7, fig.height=5, echo = FALSE, warning = FALSE}
tillotson_graph_sh
```

**SPRING-RUN THINGS**

TABLE X. Spring-run surrogate release information and loss.Last updated `r format(Sys.time(), '%m/%d/%Y')`
```{r, echo = FALSE, warning = FALSE}


table_surrogate <- tables[[8]] %>%
  dplyr::bind_rows() %>%
  janitor::clean_names(case = "upper_camel") %>%
  select(-4,-8,-14,-11) %>%
  mutate(Proportion = round((ConfirmedLoss/LossThreshold0_25PercentOfCwtReleased)*100,1)) %>%
  mutate(Loss = paste0(ConfirmedLoss,' (',Proportion,'%)'),
         'First/Last Loss' = paste0(format(as.Date(FirstLoss), '%b %d'),'/',format(as.Date(LastLoss), '%b %d'))) %>%
  select(1,2,'Release Date' = 3, 'Run' = 4, 'Release Size' = 5, 'CWT Released' = 6, 'Loss Threshold' = 7, 12,13)
  

```

```{r, echo = FALSE, warning = FALSE}
flextable(table_surrogate) %>%
  vline()%>%
  hline() %>%
  border_outer() %>%
  width(width = 1, unit = "in") %>%
  font(fontname = 'Segoe UI', part = "body") %>%
  font(fontname = 'Segoe UI Semibold', part = "header") %>%
  fontsize(size = 12, part = "header") %>%
  fontsize(size = 10, part = "body")
```